% !TeX root = ./main.tex

\chapter{Architecture}




\section{Polynomial Arithmetic}

blah blah

From the implementation perspective these polynomials are an array 
of unsigned coefficients. 
All coefficients are less than q (7681), which means 13 bits.
Each polynomial has n=255 coefficients.



\subsection{Polynomial Multiplication}


Multiplication over polynomial rings is the most 
critical operation performed in Lattice based 
cryptographic schemes.

In Standard or Random lattices the main operation is matrix-vector 
multiplication. In Ring or Ideal lattices the main operation is
polynomial multiplication. 
Module lattices lie somewhere between Standard and Ring lattices.
The main operation is multiplication of a vector of polynomials with 
another polynomial.

\section{Number Theoretic Transform}
Fast Fourier Transform where coefficients are defined in a finite field.

Performing the polynomial multiplications in NTT will transform the 
polynomial multiplication to a pointwise multiplication. This 
can reduce the time complexity from quadratic $\mathcal{O}(n^2)$  to quasi-linear ($\mathcal{O}(n\log{}n)$ serial or $\mathcal{O}(\log{}n)$ parallel),
the NTT and inverse NTT hardware could impose a large area impact 
on the design.


In Kyber all polynomials sent over the channel (Cyphertext and Public Key) are in normal domain.

NTT not needed for area constrained implementation?

Secret key is in NTT domain.


While performing the 

\section{Noise Sampling}

- Bernoulli sampling
- Cumulative Distribution Table (CDT) sampling
- Knuth
- Yao sampling
- Ziggurat sampling
- Micciancio
- Walter Gaussian Sampler


Gaussian Sampler:
Used in encryption
costly

\cite{poppelmann2014a} :
1: exp() : rejection sampling + Bernoulli trials
2: rounding-based \cite{devroye1986}

\section{Entropy Expansion?}
Keccak
FIPS 202:
cSHAKE: customizable SHAKE function
SHAKE-128 
SHAKE-256
SHA3-256
SHA3-512

customizable SHAKE function

Only need Keccak-f1600 permutation

independent streams can be pipelined.




